Calculating Entropies With Nested Sampling

### 2017-02-04 paper/ms.tex
New numbers

% These were produced with a random number seed of 0
% on commit 947317948d04255ea0baff7a7d3e357b0c2f7fcb
% With 10 particles, 1000 mcmc steps per NS iteration.

\begin{align}                    % (num_particles, mcmc_steps, max_depth, reps)
H_{\x}    &= 6.223 \pm 0.021 \\% (100, 1000, 20.0,  147)
H_{\d}    &=    \\% (100, 1000, 1200.0, 99)
H_{\x,\d} &=    \\% (100, 1000, 1200.0, 99)
\end{align}

@@

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-782.02$, and
$-788.23$ respectively.
\begin{align}
H'_{\x}     &= 1.113 \pm 0.025 \\
H'_{\d}     &= 178.4 \pm 3.7   \\
H'_{\x, \d} &= 180.4 \pm 3.4
\end{align}
and therefore a mutual information of {\query a negative value! Oh dear!
Something is wrong. Update: well I found a bug after this, so it might
change. :)}

>>>>

% These were produced with a random number seed of 0
% on commit 44525f13edd0d29de43e703db17c594fc0d5045c

\begin{align}                  % (num_particles, mcmc_steps, max_depth, reps)
H_{\x}    &= 6.223 \pm 0.021 \\% (100, 1000, 20.0,  147)
H_{\d}    &= 805.1 \pm 9.7   \\% (100, 1000, 1000.0, 52)
H_{\x,\d} &= 873   \pm 25    \\% (100, 1000, 1200.0, 12)
\end{align}

@@

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-782.02$, and
$-788.23$ respectively.
%\begin{align}
%H'_{\x}     &= 1.113 \pm 0.025 \\
%H'_{\d}     &= 178.4 \pm 3.7   \\
%H'_{\x, \d} &= 180.4 \pm 3.4
%\end{align}
and therefore a mutual information of {\query a negative value! Oh dear!
Something is wrong. Update: well I found a bug after this, so it might
change. :)}
